Eclipse Che for Fair and Easy Education

### 2019-05-09 che.tex
typos and minor

\section{Introduction}
\label{sec:Introduction}
As children we, used to look into the clouds and count sheep. 
As developers, we look into the clouds and check our applications.  
Cloud technologies are already state of the art, enabling global players like Google to run applications on a world-scale.
The market-leaders got their portfolio stocked up with  a  variety  of  different  cloud  technologies,  ranging 
from cloud computing, cloud storage, database-as-a-service or rentable authentication. 
Modern Software needs to be scalable, self-contained, and should run on any device, aswell as in the cloud.  
This trend is also visible in Googles searches \ref{fig:digdocker}.

@@

Lucky for us, a new open-source software, Eclipse Che, is on the rise to enable everyone for cloud-native development.
Che is unlike a normal eclipse distribution: 
It is hosted on a server and developers get access with their browser. 
Instead of installing dependencies, compilers etc. locally, a common workspace is set up, which is shared amongst the programmers. 
The software build is run inside a docker-container, making it cloud-native by default. 
With Version 7 upcoming and prominent support from RedHat, Eclipse Che is not a prototype anymore. 
The latest distributions of RedHats OpenShift are shipped with Che in default. 
Therefore, it is worth looking at this possible game-changer. 
With the first part of this paper, the structure and ideas of Che are explained in more detail, the second part of this paper covers general arguments about this approach and gives a detailed overview of reachable benefits for education.

@@

Eclipse Che  can be run  on any  base-technology  on  localhost – this is rather for demonstrations aswell as for developers working on the Che-Code. 
When run (locally) on docker, the plugin CheDir enables a portable workspace, 
which can be used on any docker based Che.
\subsection{Technology and Workflow}
\label{subsec:Tec}
A normal IDE is software on your computer which makes programming easier than doing it in a plain text-editor and commandline. 
Common tasks for an IDE are dependency management, debugging, refactoring and autocompletion.
It is important that an IDE is not required to develop – you can write .java-files in Vim, compile on the console and run a .Jar manually. 
With that in mind, we can see that the IDE is just a tool to make things (a lot) more comfortable – but you also have requirements such as the JDK, the .Jars you need in your classpath etc. as they are only utilized by your IDE.
You can consider this stack as your workspace as it contains everything required to work, with the IDE making the workspace comfortable to use.
Eclipse Che does not work like a normal IDE. 
Che consists of three main components shown in Figure \ref{fig:cheworkflow}\footnote{source: \url{https://en.wikipedia.org/wiki/Eclipse_Che\#/media/File:Eclipse_Che_-_Workflow.PNG}}.

@@

\subsection{Reproduction and Maintenance}
The university of Arizona showed \cite{CO16}, that about 50\% of software inspected was not able to build. 
Common reasons are missing, changed or faulty dependencies, leading to the common term of \textit{dependency hell} aswell as unclear documentation. 
Experienced programmers are usually able to overcome these issues, given enough time. This continues to be an issue \cite{CL14}, and without a different approach probably always will be.

@@

The combination of a quick setup and the usability of every enhancement makes Che especially interesting to recruit troubleshooters into your projects, which solve some of the very specialiced tasks.  
With  the  artifacts  being  reproducible,  the  expert  can quickly inspect the subject and analyse problems.
With a finished workspace he can quickly start working. 
With his changes being also in docker, they will be visible and functional for the whole team.
Therefore,  the  hardest  common  problems  regarding \textit{quick help} are addressed and solved. 
As an additional minor benefit, it is easy to hibernate resources  using  Che  with  Kubernetes  or  Openshift.
The workspaces collect metrics like any other container and are therefore scalable on demand. 
The ability of downscaling the development resources has a big impact on the overall 
workload. 
As a further example, the workspaces could be shut down out of normal business-time. This attribute is crucial for a rented infrastructure, which is paid commonly on both workload and storage. 
\subsection{Always On}
The very first handicap coming with Che is the requirement for a good internet connection. 
While your normal buro is already equipped with internet, one may want to work on train or there is simply a problem with the WiFi in your hotel.
With the possibility to setup che on localhost, you can learn the basics and routines offline. As the main benefits come in terms of teamwork, this is not a real solution.
\subsection{Knowledge Required}
The primary problem with Che is the requirement for an already dense knowledge of cloud related technology.
Setting up the Workspace, docker-images, build and CI scripts is a complex topic and can not be done by someone getting started. 
This requirement extends when working with a multipod-environment. 
While most of the tasks are by themselves rather simple, the bare amount of such tasks (especially when migrating an existing project to Che) requires a broad knowledge.
This can be done by a single expert user, enabling the other developers  to  use  the  build-routines and  environments provided. 
However, many problems which arise are related to the cloud-environement and will be hard to solve by a novice user, making him dependent on the expert. 
It's therefore necessary to get everyone on a certain base-level to solve their own problems, otherwise the expert will be overloaded and the project stuck.

@@

\section{Benefits for Education}
\label{sec:EvalEdu}
In addition to the previous mentioned benefits, there are more points about Che that are especially important for educational purposes, such as courses in the university, professional school or research departments.
For simplicity I will only elaborate universities, to which I can best relate.
\subsection{New motivational and intuitive Courses}
Eclipse Che provides the possibility to learn primary cloud-technologies hands on and in a simple and supportive manner. 
Unfortunetally, these topics are currently not widely teached at university.
Che makes it possible to teach students fundamentals of modern software development.
Depending on the courses subject, one can either provide scalable software or a running environment. 
With fitting material provided, it's easy to learn cloud-native development, DevOps or Cloud-Operations. 
Even complicated topics, like microservices and IoT-applications can easily be adaptet inside Che \cite{IV18} and performed as for example as group-projects with a common goal. 
The student will need to understand cloud-components aswell as team-work to succeed with Che.

@@

One may argue that having this kind of anticipation is extra rewarding and therefore highly motivational.
From my personal experience, working in this modus becomes exhausting after a period of weeks, especially when errors occur. 
I expect this experience to be highly personal. 
I think providing the fastest infrastructure possible, enabling the fastest results, is the better way. 
Making progress slower is much easier than making it faster.  
In addition, the time spent waiting on your machine learning algorithm or moving to the mac-laboratory on weekends is simply dead time. 
It should therefore be minimized.

>>>>

\section{Introduction}
\label{sec:Introduction}
As children we, used to look into the clouds and count sheep. 
As developers, we look into the clouds and check our applications.  
Cloud technologies are already state of the art, enabling global players like Google to run applications on a world-scale.
The market-leaders got their portfolio stocked up with  a  variety  of  different  cloud  technologies,  ranging 
from cloud computing, cloud storage, database-as-a-service or rentable authentication. 
Modern Software needs to be scalable, self-contained, and should run on any device, as well as in the cloud.  
This trend is also visible in Googles searches \ref{fig:digdocker}.

@@

Lucky for us, a new open-source software, Eclipse Che, is on the rise to enable everyone for cloud-native development.
Che is unlike a normal Eclipse-distribution: 
It is hosted on a server and developers get access with their browser. 
Instead of installing dependencies, compilers etc. locally, a common workspace is set up, which is shared amongst the programmers. 
The software build is run inside a docker-container, making it cloud-native by default. 
With Version 7 upcoming and prominent support from RedHat, Eclipse Che is not a prototype anymore. 
The latest distributions of RedHats OpenShift are shipped with Che in default. 
Therefore, it is worth looking at this possible game-changer. 
With the first part of this paper, the structure and ideas of Che are explained in more detail, the second part of this paper covers general arguments about this approach and gives a detailed overview of reachable benefits for education.

@@

Eclipse Che  can be run  on any  base-technology  on  localhost – this is rather for demonstrations as well as for developers working on the Che-Code. 
When run (locally) on docker, the plugin CheDir enables a portable workspace, 
which can be used on any docker based Che.
\subsection{Technology and Workflow}
\label{subsec:Tec}
A normal IDE is software on your computer which makes programming easier than doing it in a plain text-editor and commandline. 
Common tasks for an IDE are dependency management, debugging, refactoring and autocompletion.
It is important that an IDE is not required to develop – you can write .java-files in Vim, compile on the console and run a .Jar manually. 
With that in mind, we can see that the IDE is just a tool to make things (a lot) more comfortable – but you also have requirements such as the JDK, the .Jars you need in your classpath etc. as they are only utilized by your IDE.
You can consider this stack as your workspace as it contains everything required to work, with the IDE making the workspace comfortable to use.
Eclipse Che does not work like a normal IDE. 
Che consists of three main components shown in Figure \ref{fig:cheworkflow}\footnote{source: \url{https://en.wikipedia.org/wiki/Eclipse_Che\#/media/File:Eclipse_Che_-_Workflow.PNG}}.

@@

\subsection{Reproduction and Maintenance}
The University of Arizona showed \cite{CO16}, that about 50\% of software inspected was not able to build. 
Common reasons are missing, changed or faulty dependencies, leading to the common term of \textit{dependency hell} as well as unclear documentation. 
Experienced programmers are usually able to overcome these issues, given enough time. This continues to be an issue \cite{CL14}, and without a different approach probably always will be.

@@

The combination of a quick setup and the usability of every enhancement makes Che especially interesting to recruit troubleshooters into your projects, which solve some of the very specialiced tasks.  
With  the  artifacts  being  reproducible,  the  expert  can quickly inspect the subject and analyse problems.
With a finished workspace he can quickly start working. 
With his changes being also in docker, they will be visible and functional for the whole team.
Therefore,  the  hardest  common  problems  regarding \textit{quick help} are addressed and solved. 
As an additional minor benefit, it is easy to hibernate resources  using  Che  with  Kubernetes  or  Openshift.
The workspaces collect metrics like any other container and are therefore scalable on demand. 
The ability of downscaling the development resources has a big impact on the overall 
workload. 
As a further example, the workspaces could be shut down out of normal business-time. This attribute is crucial for a rented infrastructure, which is paid commonly on both workload and storage. 
\subsection{Always On}
The very first handicap coming with Che is the requirement for a good internet connection. 
While a common office is already equipped with internet, one may want to work on a train or there is simply a problem with the WiFi in the hotel.
With the possibility to setup Che on localhost, you can learn the basics and routines offline. As the main benefits come in terms of teamwork, this is not a real solution.
\subsection{Knowledge Required}
The primary problem with Che is the requirement for an already dense knowledge of cloud related technology.
Setting up the Workspace, docker-images, build and CI scripts is a complex topic and can not be done by someone getting started. 
This requirement extends when working with a multipod-environment. 
While most of the tasks are by themselves rather simple, the bare amount of such tasks (especially when migrating an existing project to Che) requires a broad knowledge.
This can be done by a single expert user, enabling the other developers  to  use  the  build-routines and  environments provided. 
However, many problems which arise are related to the cloud-environement and will be hard to solve by a novice user, making him dependent on the expert. 
It's therefore necessary to get everyone on a certain base-level to solve their own problems, otherwise the expert will be overloaded and the project stuck.

@@

\section{Benefits for Education}
\label{sec:EvalEdu}
In addition to the previous mentioned benefits, there are more points about Che that are especially important for educational purposes, such as courses in the university, professional school or research departments.
For simplicity I will only elaborate universities, to which I can best relate.
\subsection{New motivational and intuitive Courses}
Eclipse Che provides the possibility to learn primary cloud-technologies hands on and in a simple and supportive manner. 
Unfortunetally, these topics are currently not widely teached at university.
Che makes it possible to teach students fundamentals of modern software development.
Depending on the courses subject, one can either provide scalable software or a running environment. 
With fitting material provided, it's easy to learn cloud-native development, DevOps or Cloud-Operations. 
Even complicated topics, like microservices and IoT-applications can easily be adaptet inside Che \cite{IV18} and performed as for example as group-projects with a common goal. 
The student will need to understand cloud-components as well as team-work to succeed with Che.

@@

One may argue that having this kind of anticipation is extra rewarding and therefore highly motivational.
From experience, working in this mode becomes exhausting after a period of weeks, especially when errors occur.
While this experience is highly personal,providing the 
fastest infrastructure possible, enabling the fastest results,is the better way.
Making  progress  slower  is much easier than making it faster. 
In addition, the time spent waiting on your machine learning algorithm or moving to the mac-laboratory on weekends is simply dead time. 
It should therefore be minimized.
